Tropical Andes plant occurrence data GBIF

### 2024-05-10 code/L0/L0_TropicalAndes_plants_GBIF.Rmd
Fix column issues with gbifID and remove geometry column from occurrence output

# Set file paths
```{r}
data_path<-file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
output_path<- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
```

@@

# Download plant occurrence data from GBIF
```{r}
occ_download(
pred("taxonKey", 6),
pred("hasCoordinate", TRUE),
pred("hasGeospatialIssue", FALSE),
pred_in("country",c("EC","CO","VE", "PE", "BO")),
format = "SIMPLE_CSV"
)
```

## Retrive GBIF download, save file, and load into r
```{r}
d1 <- occ_download_get("0009835-231002084531237", path = output_path, overwrite = TRUE) %>%
  occ_download_import()
```

@@

@@

```{r}
print("The number of occurrences is")
nrow(TropicalAndes_plant_occ_forest)
print("The number of species is" )
length(unique(TropicalAndes_plant_occ_forest$species))
print("The number of genera is" )
length(unique(TropicalAndes_plant_occ_forest$genus))
print("The number of families is" )
length(unique(TropicalAndes_plant_occ_forest$family))
```

>>>>

# Set file paths
```{r}
data_path<-file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
output_path<- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
source("~/GitHub/neotropical_plants/functions/data_summary.R")
```

@@

# Download plant occurrence data from GBIF
```{r}
occ_download(
pred_in("taxonKey", c(220, 196)),
pred("hasCoordinate", TRUE),
pred("hasGeospatialIssue", FALSE),
pred_in("country",c("EC","CO","VE", "PE", "BO")),
format = "SIMPLE_CSV"
)
```

## Retrive GBIF download, save file, and load into r
```{r}
d1 <- occ_download_get("0061290-231120084113126", path = output_path, overwrite = TRUE) %>%
  occ_download_import()
```

@@

# Fix column types 
```{r}
TropicalAndes_plant_occ_forest$gbifID <- as.character(TropicalAndes_plant_occ_forest$gbifID)
TropicalAndes_plant_occ_forest$geometry <- NULL
```

@@

```{r}
data_summary(TropicalAndes_plant_occ_forest, TropicalAndes_plant_occ_forest$species, TropicalAndes_plant_occ_forest$genus, TropicalAndes_plant_occ_forest$family)
```
